---
title: "Untitled"
author: "Yang Lyu"
date: "11/10/2023"
output: pdf_document
---

```{r}
library(dplyr)
library(plotly)
```

```{r}
data <- read.csv("ab_data.csv")
```

```{r}
summary(data)
print("Number of rows in data: ")
# num of rows in data
nrow(data)
# num of missing
print("Number of missing values: ")
sum(is.na(data))
```

```{r}
mimic3d <- read.csv("mimic3d.csv")
#View(data)
nrow(mimic3d)*0.8 # take 47180 rows as training, rest 20% as  patients.csv
training <- mimic3d[1:47180,]
patients <- data[47181:nrow(mimic3d),]
```

```{r}
df <- read.csv("train_data.csv")
```

```{r}
old <- data %>% filter(landing_page == "old_page" & group == "control")
new <- data %>% filter(landing_page == "new_page" & group == "treatment")
count(old,old$converted == 1)
count(new, new$converted == 1)
```

```{r}
nrow(old)
old <- old[!duplicated(old$user_id),]
```

```{r}
old_distinct <- old %>% distinct(old$user_id, .keep_all = TRUE)
new_distinct <- new %>% distinct(new$user_id, .keep_all = TRUE)
```

```{r}
prop_old <- sum(old_distinct$converted == 1)/nrow(old_distinct)
nrow(old_distinct)
sum(old_distinct$converted==1)
prop_new <- sum(new_distinct$converted == 1)/nrow(new_distinct)
nrow(new_distinct)
sum(new_distinct$converted==1)
prop_old
prop_new
```

```{r}
prop <- data.frame(
  langing_page = c("Old Page", "New Page"),
  proportion = c(prop_old, prop_new)
)
# plot data
fig_1 <- plot_ly(
  x = prop$langing_page, 
  y = prop$proportion,
  type = "bar"
) %>% layout(yaxis = list(title = "Conversion Rate"))

fig_1
```

```{r, include=FALSE, warning=FALSE}
library(rstan)

data <- list(
  N_old = 145274,
  N_new = 145310,
  conversions_old = 17489,
  conversions_new = 17264
)

stan_code <- "
data {
  int<lower=0> N_old;
  int<lower=0> N_new;
  int<lower=0> conversions_old;
  int<lower=0> conversions_new;
}

parameters {
  real<lower=0, upper=1> p_old;
  real<lower=0, upper=1> p_new;
}

model {
  p_old ~ beta(2 + conversions_old, 20 + N_old - conversions_old);
  p_new ~ beta(2 + conversions_new, 20 + N_new - conversions_new);
}

generated quantities {
  real p_difference;
  p_difference = p_new - p_old;
}
"

stan_model <- stan_model(model_code = stan_code)

# MCMC sampling
stan_samples <- sampling(stan_model, data = data, iter = 10000, chains = 4)

# posterior result
posterior_samples <- extract(stan_samples)
p_difference <- posterior_samples$p_difference

# calculate prob of new_better
prob_new_better <- mean(p_difference > 0)

cat("\n Probability that the new page is better than the old page:", prob_new_better, "\n")

```

```{r, include=FALSE}
p_difference <- posterior_samples$p_difference
df <- data.frame(p_difference)

# plot difference density
ggplot(df, aes(x = p_difference)) +
  geom_density(fill = "blue", alpha = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  labs(title = "Probability Density",
       x = "new page rate- old page rate",
       y = "Density") +
  theme_minimal()
```

```{r, include=FALSE}
# posterior for old page
p_old <- posterior_samples$p_old
df1 <- data.frame(p_old)
# posterior for new page
p_new <- posterior_samples$p_new
df2 <- data.frame(p_new)

# plot density 
ggplot(df2) +
  geom_density(aes(x = p_old), fill = "blue", alpha = 0.5) +
  geom_density(aes(x = p_new), fill = "red", alpha = 0.5) +
  labs(title = "Probability Density",
       x = "Conversion rate",
       y = "Density") +
  annotate("text", x=0.1187, y = 300, label= "New Page") +
  annotate("text", x=0.1205, y = 300, label= "Old Page")

```

Proof of parameters in posterior:  
Let $p$ be the conversion rate, consider a series of Bernoulli distribution (every visitor has probability $p$ to convert or $(1-p)$ to not convert), $i.e. binomial(s,n|p)=\binom{n}{s}p^{s}(1-p)^{n-s}$, where $p\in[0,1]$.  
$Prior=P(p)=Beta(\alpha,\beta)$, $likelihood=P(s|p)=\binom{n}{s}p^{s}(1-p)^{n-s}$.  
By Bayesian: $P(p|s)=\frac{P(s|p) \cdot P(p)}{P(s)}$,  
$P(s)=\int P(s|p) \cdot P(p)dp$  
$=\int_{0}^{1}\binom{n}{s}p^{s}(1-p)^{n-s}\frac{1}{B(\alpha,\beta)}p^{\alpha-1}(1-p)^{\beta-1}dp$  
$=\frac{\binom{n}{s}}{B(\alpha,\beta)}\int_{0}^{1}p^{s+\alpha-1}(1-p)^{n-s+\beta-1}dp$  
$=\binom{n}{s}\frac{B(s+\alpha,n+\beta-s)}{B(\alpha,\beta)}\int_{0}^{1}\underbrace{\frac{1}{B(s+\alpha,n+\beta-s)}p^{s+\alpha-1}(1-p)^{n+\beta-s-1}}_{this\ is \ a \ Beta \ with \ parameters\  s+\alpha,n+\beta-s}dp$  
$=\binom{n}{s}\frac{B(\alpha+s,\beta+n-s)}{B(\alpha,\beta)} \underbrace{\int_{0}^{1}Beta(\alpha+s,\beta+n-s)dp}_{=1\ since\ integral\ on\ [0,1]\ is\ 1\ for\ Beta}$  
$=\binom{n}{s}\frac{B(\alpha+s,\beta+n-s)}{B(\alpha,\beta)}$  
Hence, $P(p|s)=\frac{P(s|p) \cdot P(p)}{P(s)}$  
$=\frac{\binom{n}{s}p^{s}(1-p)^{n-s}\frac{1}{B(\alpha,\beta)}p^{\alpha-1}(1-p)^{\beta-1}}{\binom{n}{s}\frac{B(\alpha+s,\beta+n-s)}{B(\alpha,\beta)}}$  
$=\frac{1}{B(\alpha+s,\beta+n-s)}p^{\alpha+s-1}(1-p)^{\beta+n-s-1}$  
$=Beta(\alpha+s,\beta+n-s)$  

```{r}
old_distinct <- old %>% distinct(old$user_id, .keep_all = TRUE)
new_distinct <- new %>% distinct(new$user_id, .keep_all = TRUE)
visitor_to_old <- nrow(old_distinct)
visitor_to_new <- nrow(new_distinct)
conversion_old <- sum(old_distinct$converted)
conversion_new <- sum(new_distinct$converted)

alpha_prior <- 2
beta_prior <- 20

# calculate posterior
posterior_old <- rbeta(1000000, alpha_prior+conversion_old, beta_prior+visitor_to_old-conversion_old)
posterior_new <- rbeta(1000000, alpha_prior+conversion_new, beta_prior+visitor_to_new-conversion_new)

# calculate prob of new rate > old rate
mean(posterior_new > posterior_old)

#Riemann sum as safety check:
sapply(seq(0.001,0.999, length.out=1000000), function(x){
    dbeta(x, alpha_prior+conversion_new,beta_prior+visitor_to_new-conversion_new)*
      pbeta(x, alpha_prior+conversion_old, beta_prior+visitor_to_old-conversion_old)})%>%sum()/1000000

```

```{r}
posterior_Old <- data.frame(old_rate=c(posterior_old))
posterior_New <- data.frame(new_rate=c(posterior_new))
mean_old <- mean(posterior_Old$old_rate)
mean_new <- mean(posterior_New$new_rate)
cat("Mean of conversion rate on old page is", mean_old, "\n")
cat("Mean of conversion rate on new page is", mean_new, "\n")
```

```{r}
# plot density 
fig_2 <- ggplot() +
  geom_density(aes(x = posterior_Old$old_rate), fill = "blue", alpha = 0.5) +
  geom_density(aes(x = posterior_New$new_rate), fill = "red", alpha = 0.5) +
  geom_vline(xintercept = mean_old, linetype = "dashed", color = "blue") +
  geom_vline(xintercept = mean_new, linetype = "dashed", color = "red") +
  labs(title = "Probability Density Comparison", subtitle = "New page vs. old page",
       x = "Conversion rate",
       y = "Density") +
  annotate("text", x = 0.1187, y = 300, label= "New Page") +
  annotate("text", x = 0.1205, y = 300, label= "Old Page") +
  annotate("text", x = mean_old, y = 0, label = paste("mean of old\n", round(mean_old, 6)), vjust = 0.5, size = 3) +
  annotate("text", x = mean_new, y = 0, label = paste("mean of new\n", round(mean_new, 6)), vjust = 0.5, size = 3) +
  annotate("segment", x = mean_old, xend = mean_new, y = 500, yend = 500, colour = "black", linewidth = 2, arrow = arrow()) +
  annotate("text", x = (mean_old + mean_new)/2, y = 480, label = paste(round(mean_old-mean_new,6))) +
  scale_color_manual(values = c("red", "blue"), labels = c("new page", "old page"))

fig_2
```

```{r}
old_distinct <- old %>% distinct(old$user_id, .keep_all = TRUE)
new_distinct <- new %>% distinct(new$user_id, .keep_all = TRUE)
alpha_prior <- 2
beta_prior <- 20
sub_old <- data.frame()
sub_new <- data.frame()
result <- data.frame()
for(i in seq(100, 145174, by = 100)){
  sampled_old <- old_distinct %>% sample_n(100) # sampling 100 rows from origin data
  sampled_new <- new_distinct %>% sample_n(100) 
  sub_old <- bind_rows(sub_old,sampled_old) # add sample to subset
  sub_new <- bind_rows(sub_new,sampled_new) 
  old_distinct <-anti_join(old_distinct,sampled_old) # drop sample from origin data
  new_distinct <-anti_join(new_distinct,sampled_new)
  visitor_to_old <- nrow(sub_old)
  visitor_to_new <- nrow(sub_new)
  conversion_old <- sum(sub_old$converted)
  conversion_new <- sum(sub_new$converted)
  # calculate posterior
  posterior_old <- rbeta(1000000, alpha_prior+conversion_old, beta_prior+visitor_to_old-conversion_old)
  posterior_new <- rbeta(1000000, alpha_prior+conversion_new, beta_prior+visitor_to_new-conversion_new)
  # calculate prob of new rate > old rate
  value <- mean(posterior_new > posterior_old)
  sample_result <- rbind(c(i,value))
  result <- rbind(result, sample_result) # store df with i's and values
}
View(result)
```

```{r}
plot(result)
```